A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.  We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.  The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.  Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.  Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.

As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.  This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.

The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.

Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.  This deformation gives the desired theory.  The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.  Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.

\end{proof}

@@

There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.

>>>>

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.  Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.

We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
\begin{equation}
\label{eq:4d_12_general_def}
\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
\end{equation}
First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.  This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.

Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.  The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.  To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.  We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.  The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.  Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.  Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.

As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.  Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.  That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.

It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.  To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.  Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.  Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.

We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.  The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
\end{equation}
in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.

Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.  This deformation gives the desired theory.  The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.  Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
\end{proof}

@@

There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
